Development of Performance Regression Analysis Tool using Distributed Tracing on Microservice-based Application\\

### 2022-06-23 paper.tex
txs auto checkin

\subsection{A Real-time Trace-level Root-cause Diagnosis System in Alibaba Datacenters}
This study \cite{rca-alibaba} uses distributed tracing to perform
Diagnostics of performance degradation on a system by performing graph analysis on
trace level in real-time to determine the root cause of performance degradation or
root cause. This approach was developed based on performance profiling, tracking, and logging system in Alibaba datacenter to speed up root cause diagnosis in real-time. The developed system allows the discovery of normative patterns and corresponding key graph properties, which are saved and updated offline as a knowledge base for further use in risk estimation at the trace level and identify transitions that are unexpected deviations from the normal
normal as shown in Fig. \ref{rc}.
\begin{figure}[htb]
	\centering
	\includegraphics[width=0.5\textwidth]{resources/ch2/rca-framework.png}
	\caption{Workflow of Root-cause Analysis on \cite{rca-alibaba}}
	\label{rca-framwork}
\end{figure}

@@

For testing purposes, 3 significant levels or alpha will be used, those are 0.1, 0.05, and 0.001. These three significant levels are used for knowing the sensitivity of the regression detection results with interpretation that the smaller the value of
significant levels, the more significant the evidence to reject $h_{0}$. Significant value 0.1
was chosen as the upper limit of the significant value to determine the sensitivity level of test case with the greatest significant value. While the value of 0.05 was chosen because this value is the most commonly used value as a significant value on the statistical test of the hypothesis. While the value of 0.001 was chosen as a comparison of the value of least significant to test the lower limit of the significant value.

\begin{table}[!htb]
	\caption{Test Cases}
	\label{testcases}
	\centering
	\begin{tabular}{|l|l|c|c|l|}
		\hline
		\textbf{ID} &
		\textbf{Service/Function} &
		\multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Extra \\ Latency\end{tabular}}} &
		\multicolumn{1}{l|}{\textbf{User}} &
		\textbf{Description} \\ \hline
		IS1 &
		CheckoutService/PlaceOrder &
		100ms &
		25 &
		Extra latency case \#1 \\ \hline
		IS2 &
		CheckoutService/PlaceOrder &
		250ms &
		25 &
		Extra latency case \#2 \\ \hline
		IS3 &
		CheckoutService/PlaceOrder &
		350ms &
		25 &
		Extra latency case \#3 \\ \hline
		IS4 &
		CheckoutService/PlaceOrder &
		250ms &
		75 &
		\begin{tabular}[c]{@{}l@{}}Extra latency with\\ increased user\end{tabular} \\ \hline
		IS5 &
		CheckoutService/PlaceOrder &
		250ms &
		150 &
		\begin{tabular}[c]{@{}l@{}}Extra latency with\\ increased user\end{tabular} \\ \hline
		IS6 &
		CheckoutService/PlaceOrder &
		- &
		25 &
		Extra CPU case \\ \hline
		\multirow{5}{*}{IS7} &
		CheckoutService/PlaceOrder &
		\multirow{5}{*}{250ms} &
		\multirow{5}{*}{25} &
		\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Extra latency case\\ with multiple \\ services\end{tabular}} \\ \cline{2-2}
		&
		ProductCatalog/GetProduct &
		&
		&
		\\ \cline{2-2}
		&
		ProductCatalog/ListProducts &
		&
		&
		\\ \cline{2-2}
		&
		ShippingService/GetQuote &
		&
		&
		\\ \cline{2-2}
		&
		\begin{tabular}[c]{@{}l@{}}RecommendationService/\\ ListRecommendations\end{tabular} &
		&
		&
		\\ \hline
		ES1 &
		All Normal &
		- &
		75 &
		\begin{tabular}[c]{@{}l@{}}No extra latency\\ with increased user \#1\end{tabular} \\ \hline
		ES2 &
		All Normal &
		- &
		150 &
		\begin{tabular}[c]{@{}l@{}}No extra latency\\ with increased user \#2\end{tabular} \\ \hline
		ES3 &
		\begin{tabular}[c]{@{}l@{}}Checkout load\\ increased to 100 in Loadgen\end{tabular} &
		- &
		25 &
		\begin{tabular}[c]{@{}l@{}}Increased external\\ load case \#1\end{tabular} \\ \hline
		ES4 &
		\begin{tabular}[c]{@{}l@{}}Curency load \\ increased to 100 in Loadgen\end{tabular} &
		- &
		25 &
		\begin{tabular}[c]{@{}l@{}}Increased external\\ load case \#2\end{tabular} \\ \hline
	\end{tabular}
\end{table}

\subsection{Experiment Result}
The following tables \ref{test-1} \ref{test-2} \ref{test-3} describe the summaries of the experiment results that have been performed with three different alpha values. The result is on all test cases, IS2 cases to IS4 cases were successfully detected by regression and critical path analysis is appropriate. It's just that for the SI1 case, only the alpha value is 0.1
which can successfully detect the regression and determine the source of the cause of the regression with critical path analysis. Other alpha values cannot detect regression and do not perform critical path analysis.

\begin{table}[!htb]
	\caption{Experiment Result for Alpha of 0.1}
	\label{test-1}
	\centering
	\begin{tabular}{|l|c|c|}
		\hline
		\textbf{ID} & \multicolumn{1}{l|}{\textbf{Regression Detected}} & \multicolumn{1}{l|}{\textbf{Critical Path Analysis Correct}} \\ \hline
		IS1 & Yes & Yes \\ \hline
		IS2 & Yes & Yes \\ \hline
		IS3 & Yes & Yes \\ \hline
		IS4 & Yes & Yes \\ \hline
		IS5 & Yes & Yes \\ \hline
		IS6 & Yes & Yes \\ \hline
		IS7 & Yes & Yes \\ \hline
		ES1 & Yes & Yes \\ \hline
		ES2 & Yes & Yes \\ \hline
		ES3 & Yes & Yes \\ \hline
		ES4 & Yes & Yes \\ \hline
	\end{tabular}
\end{table}

\begin{table}[!htb]
	\caption{Experiment Result for Alpha of 0.05}
	\label{test-2}
	\centering
	\begin{tabular}{|l|c|c|}
		\hline
		\textbf{ID} & \multicolumn{1}{l|}{\textbf{Regression Detected}} & \multicolumn{1}{l|}{\textbf{Critical Path Analysis Correct}} \\ \hline
		IS1 & No & No \\ \hline
		IS2 & Yes & Yes \\ \hline
		IS3 & Yes & Yes \\ \hline
		IS4 & Yes & Yes \\ \hline
		IS5 & Yes & Yes \\ \hline
		IS6 & Yes & Yes \\ \hline
		IS7 & Yes & Yes \\ \hline
		ES1 & Yes & Yes \\ \hline
		ES2 & Yes & Yes \\ \hline
		ES3 & Yes & Yes \\ \hline
		ES4 & Yes & Yes \\ \hline
	\end{tabular}
\end{table}
\begin{table}[!htb]
	\caption{Experiment Result for Alpha of 0.001}
	\label{test-3}
	\centering
	\begin{tabular}{|l|c|c|}
		\hline
		\textbf{ID} & \multicolumn{1}{l|}{\textbf{Regression Detected}} & \multicolumn{1}{l|}{\textbf{Critical Path Analysis Correct}} \\ \hline
		IS1 & No & No \\ \hline
		IS2 & Yes & Yes \\ \hline
		IS3 & Yes & Yes \\ \hline
		IS4 & Yes & Yes \\ \hline
		IS5 & Yes & Yes \\ \hline
		IS6 & Yes & Yes \\ \hline
		IS7 & Yes & Yes \\ \hline
		ES1 & Yes & Yes \\ \hline
		ES2 & Yes & Yes \\ \hline
		ES3 & Yes & Yes \\ \hline
		ES4 & Yes & Yes \\ \hline
	\end{tabular}
\end{table}

@@

\subsection{Overhead Testing}
Of the 11 test cases, the average PRA Engine tool uses 0.046
vCPU with standard deviation of 0.0038 and 154.41 MiB Memory with standard
deviation of 17.91 in one analysis. The entire cluster has resources
as much as 6 vCPUs and 22.5 GiB, so that in one time doing PRA Engine analysis
resulting in CPU overhead as much as 0.78\% and Memory as much as 0.67\% to the Kubernetes cluster. Overhead caused by the tool is low so that the use of PRA Engine tools will have no impact on the overall performance of the Kubernetes cluster. Table \ref{overhead-tbl} shows the result of the overhead testing.
\begin{table}[!htb]
	\caption{Overhead testing result}
	\label{overhead-tbl}
	\centering
	\begin{tabular}{|l|c|c|}
		\hline
		ID & CPU (vCPU) & Memory (MiB) \\
		\textbf{IS1}     & 0,042 & 137,82  \\ \hline
		\textbf{IS2}     & 0,043 & 128,71  \\ \hline
		\textbf{IS3}     & 0,04  & 131,55  \\ \hline
		\textbf{IS4}     & 0,045 & 146,6   \\ \hline
		\textbf{IS5}     & 0,046 & 153,61  \\ \hline
		\textbf{IS6}     & 0,047 & 152,71  \\ \hline
		\textbf{IS7}     & 0,048 & 152,71  \\ \hline
		\textbf{ES1}     & 0,049 & 168,8   \\ \hline
		\textbf{ES2}     & 0,05  & 183,68  \\ \hline
		\textbf{ES3}     & 0,051 & 176,59  \\ \hline
		\textbf{ES4}     & 0,052 & 165,75  \\ \hline
		\textbf{Average} & 0,046 & 154,411 \\ \hline
		\textbf{STD}     & 0,038 & 17,916  \\ \hline
	\end{tabular}
\end{table}
\pagebreak

>>>>

\subsection{A Real-time Trace-level Root-cause Diagnosis System in Alibaba Datacenters}
This study \cite{rca-alibaba} uses distributed tracing to perform
Diagnostics of performance degradation on a system by performing graph analysis on
trace level in real-time to determine the root cause of performance degradation or
root cause. This approach was developed based on performance profiling, tracking, and logging system in Alibaba datacenter to speed up root cause diagnosis in real-time. The developed system allows the discovery of normative patterns and corresponding key graph properties, which are saved and updated offline as a knowledge base for further use in risk estimation at the trace level and identify transitions that are unexpected deviations from the normal
normal as shown in Fig. \ref{rca-framwork}.
\begin{figure}[htb]
	\centering
	\includegraphics[width=0.5\textwidth]{resources/ch2/rca-framework.png}
	\caption{Workflow of Root-cause Analysis on \cite{rca-alibaba}}
	\label{rca-framwork}
\end{figure}

@@

For testing purposes, 3 significant levels or alpha will be used, those are 0.1, 0.05, and 0.001. These three significant levels are used for knowing the sensitivity of the regression detection results with interpretation that the smaller the value of
significant levels, the more significant the evidence to reject $h_{0}$. Significant value 0.1
was chosen as the upper limit of the significant value to determine the sensitivity level of test case with the greatest significant value. While the value of 0.05 was chosen because this value is the most commonly used value as a significant value on the statistical test of the hypothesis. While the value of 0.001 was chosen as a comparison of the value of least significant to test the lower limit of the significant value.
\subsection{Experiment Result}
The following tables \ref{test-1} \ref{test-2} \ref{test-3} describe the summaries of the experiment results that have been performed with three different alpha values. The result is on all test cases, IS2 cases to IS4 cases were successfully detected by regression and critical path analysis is appropriate. It's just that for the SI1 case, only the alpha value is 0.1
which can successfully detect the regression and determine the source of the cause of the regression with critical path analysis. Other alpha values cannot detect regression and do not perform critical path analysis.

\pagebreak
\begin{table}[htb]
	\caption{Test Cases}
	\label{testcases}
%	\centering
	\begin{tabular}{|l|l|c|c|l|}
		\hline
		\textbf{ID} &
		\textbf{Service/Function} &
		\multicolumn{1}{l|}{\textbf{\begin{tabular}[c]{@{}l@{}}Extra \\ Latency\end{tabular}}} &
		\multicolumn{1}{l|}{\textbf{User}} &
		\textbf{Description} \\ \hline
		IS1 &
		CheckoutService/PlaceOrder &
		100ms &
		25 &
		Extra latency case \#1 \\ \hline
		IS2 &
		CheckoutService/PlaceOrder &
		250ms &
		25 &
		Extra latency case \#2 \\ \hline
		IS3 &
		CheckoutService/PlaceOrder &
		350ms &
		25 &
		Extra latency case \#3 \\ \hline
		IS4 &
		CheckoutService/PlaceOrder &
		250ms &
		75 &
		\begin{tabular}[c]{@{}l@{}}Extra latency with\\ increased user\end{tabular} \\ \hline
		IS5 &
		CheckoutService/PlaceOrder &
		250ms &
		150 &
		\begin{tabular}[c]{@{}l@{}}Extra latency with\\ increased user\end{tabular} \\ \hline
		IS6 &
		CheckoutService/PlaceOrder &
		- &
		25 &
		Extra CPU case \\ \hline
		\multirow{5}{*}{IS7} &
		CheckoutService/PlaceOrder &
		\multirow{5}{*}{250ms} &
		\multirow{5}{*}{25} &
		\multirow{5}{*}{\begin{tabular}[c]{@{}l@{}}Extra latency case\\ with multiple \\ services\end{tabular}} \\ \cline{2-2}
		&
		ProductCatalog/GetProduct &
		&
		&
		\\ \cline{2-2}
		&
		ProductCatalog/ListProducts &
		&
		&
		\\ \cline{2-2}
		&
		ShippingService/GetQuote &
		&
		&
		\\ \cline{2-2}
		&
		\begin{tabular}[c]{@{}l@{}}RecommendationService/\\ ListRecommendations\end{tabular} &
		&
		&
		\\ \hline
		ES1 &
		All Normal &
		- &
		75 &
		\begin{tabular}[c]{@{}l@{}}No extra latency\\ with increased user \#1\end{tabular} \\ \hline
		ES2 &
		All Normal &
		- &
		150 &
		\begin{tabular}[c]{@{}l@{}}No extra latency\\ with increased user \#2\end{tabular} \\ \hline
		ES3 &
		\begin{tabular}[c]{@{}l@{}}Checkout load\\ increased to 100 in Loadgen\end{tabular} &
		- &
		25 &
		\begin{tabular}[c]{@{}l@{}}Increased external\\ load case \#1\end{tabular} \\ \hline
		ES4 &
		\begin{tabular}[c]{@{}l@{}}Curency load \\ increased to 100 in Loadgen\end{tabular} &
		- &
		25 &
		\begin{tabular}[c]{@{}l@{}}Increased external\\ load case \#2\end{tabular} \\ \hline
	\end{tabular}
\end{table}

@@

\subsection{Overhead Testing}
Of the 11 test cases, the average PRA Engine tool uses 0.046
vCPU with standard deviation of 0.0038 and 154.41 MiB Memory with standard
deviation of 17.91 in one analysis. The entire cluster has resources
as much as 6 vCPUs and 22.5 GiB, so that in one time doing PRA Engine analysis
resulting in CPU overhead as much as 0.78\% and Memory as much as 0.67\% to the Kubernetes cluster. Overhead caused by the tool is low so that the use of PRA Engine tools will have no impact on the overall performance of the Kubernetes cluster. Tab. \ref{overhead-tbl} shows the result of the overhead testing.
\begin{table}[!htb]
	\caption{Overhead testing result}
	\label{overhead-tbl}
	\centering
	\begin{tabular}{|l|c|c|}
		\hline
		\multicolumn{1}{|l|}{ID} & \multicolumn{1}{l|}{CPU (vCPU)} & \multicolumn{1}{l|}{Memory (MiB)} \\ \hline
		\textbf{IS1}     & 0,042 & 137,82  \\ \hline
		\textbf{IS2}     & 0,043 & 128,71  \\ \hline
		\textbf{IS3}     & 0,04  & 131,55  \\ \hline
		\textbf{IS4}     & 0,045 & 146,6   \\ \hline
		\textbf{IS5}     & 0,046 & 153,61  \\ \hline
		\textbf{IS6}     & 0,047 & 152,71  \\ \hline
		\textbf{IS7}     & 0,048 & 152,71  \\ \hline
		\textbf{ES1}     & 0,049 & 168,8   \\ \hline
		\textbf{ES2}     & 0,05  & 183,68  \\ \hline
		\textbf{ES3}     & 0,051 & 176,59  \\ \hline
		\textbf{ES4}     & 0,052 & 165,75  \\ \hline
		\textbf{Average} & 0,046 & 154,411 \\ \hline
		\textbf{STD}     & 0,038 & 17,916  \\ \hline
	\end{tabular}
\end{table}
\pagebreak
